\documentclass{Resume}

\usepackage{amsmath, amssymb}


\begin{document}

\makecvtitle


\section{Education \faBook}
	\cventry{2012--2016}{Electronics and Communication Engineering}{Sri Jayachamarajendra College of Engineering}{Mysore, KA}{CGPA(Until $6^{th}$ sem): \textbf{9.45/10.00}}{}
		\begin{itemize}
			%\item Currently pursuing Under graduation in Electronics and Communication.
			\item Field of interest: Digital Image Processing, Machine Learning, Computer Vision, Robotics.
		\end{itemize}
	\cventry{2010-2012}{Electronics}{Sadvidya Composite Pre-University College}{Mysore, KA}{Score: \textbf{99/100}, Overall Percentage: \textbf{94\%}}{}
	\cventry{2009-2010}{School}{Mysore West Lions Sevenaikethan School, CBSE Board}{Mysore, KA}{GPA: \textbf{10.00/10.00}, Percentile: \textbf{99.2305}}{}


\section{Work  \faSuitcase}
\cvitemwithcomment{YUVA}{Assisted for an NGO.}{\textit{November 2012- Feburary 2013}}
{Yuva, initiates in solar lamp deployment in rural areas, with prior surveys of the areas to be facilitated with led powered lighting.}
{Successfully, completed house lighting for 30 houses, within a span of three days.}

\section{Skills \faBolt}

\subsection{Open source libraries}
\cvlistitem{OpenCV, EmguCV, SimpleCV, OpenNI}

\subsection{Programming}
\cvlistdoubleitem{Visual C++\textbackslash C\#}{ Python }
\cvlistdoubleitem{C, Data Structures}{MATLAB\textbackslash Octave}
\cvlistdoubleitem{VHDL \& Verilog}{LabView \& Proteus VSM}
\cvlistdoubleitem{Assembly level languages: 8086, 8051}{Arduino Wiring}
\cvlistdoubleitem{\LaTeX}{Microsoft Office}

\subsection{Photography}
\cvlistitem{Graphic Suite: Adobe Photoshop, Adobe Lightroom}
%\cvlistitem {Accomplished winning 37 awards on Pixoto for 8 photos.}
{Photography enthusiast, hobbyist, working on the concepts of Computational Photography.}

\subsection{Cinematography and Motion graphics}
\cvlistitem{Graphic Suite: Adobe Premeire Pro, After effects, Cyberlink Power Director}
{Directed and cinematographed, a music video.}

\subsection{Languages Spoken}
\cvlistitem{English, Kannada, Hindi, Telugu}

\section{Courses \faCogs}
\cvitemwithcomment{Machine Learning by Dr. Andrew Ng, Stanford University}{Machine Learning}{Coursera - Ongoing}
\begin{itemize}
\item Concepts : Linear Algebra, Linear Regression, Logistic Regression, Neural Networks.
\item Algorithms : Gradient descent, Regularization.
\end{itemize}
\cvitemwithcomment{Programming for Everybody by Dr. Charles Severance, University of Michigan}{Python}{Coursera}
\begin{itemize}
\item Concepts : Importance of Programming, Functions, File handling, Dictionary, Tuples. \\
\end{itemize}

\section{Projects \faLightbulb}

\cvitemwithcomment{Braille Image Character Detection}{Hindi Braille Image Processing. }{OpenCV}
\begin{itemize} 
\item Key Features: Robust and faster than template matching.
\end{itemize}
{Devised an algorithm and a code in C++ for Hindi Braille image processing using OpenCV libraries, to identify the characters and to predict the text ouput. Implemented on Raspberry Pi 2 using Debian wheezy Linux Distro and SSH tunnelling to get a remote desktop connection.\\}

\cvitemwithcomment{SURF Detection}{Designed a Windows forms application for object detection.}{Visual C\# .Net}
{Based on an international paper, Speeded- Up Robust Features(SURF) was successfully implemented using EmguCV .Net wrapper. It can detect trained image from a master image or a video, 
novel scale- \& rotation-invariant detector and descriptor.\\}

\cvitemwithcomment{RFID Based Attendance Monitoring System}{Arduino UNO powered system.}{Arduino Wiring}
\begin{itemize}
\item Secured highest score 98/100 in Design and Implementation lab, equivalent to S grade.
\end{itemize}
{ Project presents a microcontroller based real time automatic attendance register system with the use of RFID
technology, it also automates the process of taking attendance and thus, prevents fraudulent entries. \\}

\cvitemwithcomment{OCR using Tessaract}{Designed a Windows forms application for OCR}{Visual C\# .Net}
{Built an application of OCR using EmguCV library(Tessaract) which can be used in Industries for printed content verification on products and it can successfully identify the text present in an image. \\}

\cvitemwithcomment{Minimalistic Browser}{Simple browser which securely uses Google search engine.}{Windows 8.1 App}
{Phone application which provides dedicated Google search bar and a direct link to Google applications, such as Gmail, Drive and YouTube.\\}

\cvitemwithcomment{Movie Ticket Booking System}{C- code project.}{Data structures in C}
{Developed a console application for a simpler ticket booking system using the concepts of data structures in C, which emphasizes on local database created using a linked list to store the User's information. }

\section{Achievements \faBullseye}

\cvitemwithcomment{Trekking}{Great Thar national desert trekking expedition, Jaisalmer, Rajsthan.}{Dec 2014 - Jan 2015}{Adevnture trekking organised by Youth hostels association of India.}\\
\cvitemwithcomment{Photography}{Online photography contest.}{Pixoto- Ongoing}{Accomplished winning 37 awards on Pixoto for 8 photos. \\ \url{http://www.pixoto.com/mr.pavannaidu}}

\cvitemwithcomment{Sports Championship}{Individual Sports Champion}{2009 - 2010}
{Won individual sports championship for two consecutive years in high school}



\section{}

\end{document}


